---
title: "KPT-org (Hu) SeqWell"
author: "BEM"
---

### Metadata

* Human organoids (Sato protocol) +/- 160 nM KPT-330 over 6 days
* All donor/treat organoids pooled+hashed run on 4 identical seq-well arrays per V4 protocol, all seq'd on Next-seq 
* seq-well runs:
  + Samples 1-4

### Preprocessing

Seurat V3 objects (per array) following DropSeq QC + Doublet removal (hashing demulti) - Combining + annotating with SCT

#### Load packages
```{r setup, include=FALSE}
Sys.setenv(PATH = paste("/Users/bemead/anaconda3/bin", Sys.getenv("PATH"), sep=":"))
library(tidyverse, quietly = T)
library(Seurat, quietly = T)
library(DescTools)
library(scales)
library(ggplot2)
library(superheat)
library(Matrix)
library(piano)
library(RColorBrewer)
library(viridis)
library(effectsize)
library(crunch)
library(progeny)
library(dorothea)
library(viper)
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

#### Merged matrix for Alexandria submission
```{r}
KPT_m = readRDS('2_Full annotation/SCT_HuOrgKPT_m_20210211.rds')

#Extract out log norm + raw counts
raw_df = as.data.frame(as.matrix(KPT_m@assays$RNA@data))
rownames = row.names(raw_df)
raw_df_with_rownames = data.frame(GENE = rownames, raw_df)
colnames(raw_df_with_rownames) = c('GENE', colnames(raw_df))
raw_exp_filename = "2_Full annotation/alexandria/hu_org_KPT_normalized_expression_counts.csv.gz"
write.csv.gz(x=raw_df_with_rownames, file=raw_exp_filename, quote = F,row.names = F)

raw_df = as.data.frame(as.matrix(KPT_m@assays$RNA@counts))
rownames = row.names(raw_df)
raw_df_with_rownames = data.frame(GENE = rownames, raw_df)
colnames(raw_df_with_rownames) = c('GENE', colnames(raw_df))
raw_exp_filename = "2_Full annotation/alexandria/hu_org_KPT_raw_expression_counts.csv.gz"
write.csv.gz(x=raw_df_with_rownames, file=raw_exp_filename, quote = F,row.names = F)

#Extract out UMAP coord
umap = rownames_to_column(as.data.frame(as.matrix(KPT_m@reductions$umap@cell.embeddings)), var = "NAME")
umap = bind_cols(umap, as.data.frame(KPT_m@meta.data$annotate), as.data.frame(KPT_m@meta.data$treat), as.data.frame(KPT_m@meta.data$donor))
umap$cell_subset = umap$`KPT_m@meta.data$annotate`
umap$`KPT_m@meta.data$annotate` = NULL
umap$donor_id = umap$`KPT_m@meta.data$donor`
umap$`KPT_m@meta.data$donor` = NULL
umap$treat = umap$`KPT_m@meta.data$treat`
umap$`KPT_m@meta.data$treat` = NULL

filename = "2_Full annotation/alexandria/hu_org_KPT_UMAP_coord.csv"
write.csv(x=umap, file=filename, quote = F,row.names = F)

#finalize metadata
metadata = KPT_m@meta.data[,c(6:7,12:13,33)]
metadata$biosample_id = metadata$hash.ID 
metadata$hash.ID = NULL
metadata$donor[which(metadata$donor == 3)] = 2
metadata$donor[which(metadata$donor == 4)] = 3
metadata$donor_id = metadata$donor 
metadata$donor = NULL
metadata$cell_subset = metadata$annotate
metadata$annotate = NULL
metadata$sex = 'female'
metadata$sex[which(metadata$donor == 3)] = 'male'

metadata$species = 'NCBITaxon_9606'
metadata$species__ontology_label = 'Homo sapiens'
metadata$disease = 'PATO_0000461'
metadata$disease__ontology_label = 'normal'
metadata$organ = 'UBERON_0002114'
metadata$organ__ontology_label = 'duodenum'
metadata$library_preparation_protocol = 'EFO_0008919'
metadata$library_preparation_protocol__ontology_label = 'Seq-Well'

metadata = rownames_to_column(metadata, var = "NAME")
filename = "2_Full annotation/alexandria/Hu_intest_metadata.csv"
write.csv(x=metadata, file=filename, quote = F,row.names = F)

```

#### SCTransform | PCA | Cluster | Project
```{r}
# Load Objects 
KPT_m = readRDS('1_Preprocess/HuOrgKPT_QC_DF_BEM_20210131.rds')
KPT_m = merge(KPT_m[[1]], KPT_m[2:4])
KPT_m = SCTransform(KPT_m, verbose = F)
KPT_m = RunPCA(KPT_m, verbose = F)
ElbowPlot(KPT_m)

KPT_m$treat = gsub("-.*","",KPT_m$hash.ID)
KPT_m$donor = gsub(".*-","",KPT_m$hash.ID)

#18 & 0.5 - looks good
dim = c(1:18)
KPT_m = FindNeighbors(KPT_m, dims = dim, k.param = ceiling(0.5*sqrt(ncol(KPT_m))), verbose = F)
KPT_m = FindClusters(KPT_m, resolution = 0.5, verbose = F)
KPT_m = RunUMAP(KPT_m, reduction = "pca", dims = dim, verbose = F, umap.method = "umap-learn")
  
pdf("2_Full annotation/plots/20210209_SCT_HuOrgKPT_m_UMAP_1.pdf")
DimPlot(KPT_m)
DimPlot(KPT_m, reduction = "umap", split.by = "treat")
DimPlot(KPT_m, reduction = "umap", split.by = "donor")
dev.off()
```

#### Subcluster
```{r}
KPT_sub = subset(KPT_m, subset = seurat_clusters == 6)

KPT_sub = SCTransform(KPT_sub, verbose = F)
KPT_sub = RunPCA(KPT_sub, verbose = F)
ElbowPlot(KPT_sub)

dim = c(1:8)
KPT_sub = FindNeighbors(KPT_sub, dims = dim, k.param = ceiling(0.5*sqrt(ncol(KPT_sub))), verbose = F)
KPT_sub = FindClusters(KPT_sub, resolution = 0.3, verbose = F)
KPT_sub = RunUMAP(KPT_sub, reduction = "pca", dims = dim, verbose = F, umap.method = "umap-learn")

DimPlot(KPT_sub)
DimPlot(KPT_sub, split.by = 'donor')
DimPlot(KPT_sub, split.by = 'treat')
FeaturePlot(KPT_sub, features = c("TFF3", "LYZ", "CHGA"))
VlnPlot(KPT_sub, features = c("TFF3", "LYZ", "CHGA", "OLFM4"))

KPT_sub2 = subset(KPT_sub, subset = seurat_clusters == 2)

KPT_sub2 = SCTransform(KPT_sub2, verbose = F)
KPT_sub2 = RunPCA(KPT_sub2, verbose = F, npcs = 10)
ElbowPlot(KPT_sub2)

dim = c(1:5)
KPT_sub2 = FindNeighbors(KPT_sub2, dims = dim, k.param = ceiling(0.5*sqrt(ncol(KPT_sub2))), verbose = F)
KPT_sub2 = FindClusters(KPT_sub2, resolution = 0.3, verbose = F)
FeatureScatter(KPT_sub2, feature1 = "TFF3", feature2 = "CHGA")

Gob = Cells(subset(KPT_sub2, idents = 1))
EEC = Cells(subset(KPT_sub2, idents = c(0,2)))

KPT_m$new_clusters = KPT_m$seurat_clusters

my_levels = c(0, 1, 2, 3, 4, 5, 6, 7, 8)

KPT_m@meta.data$new_clusters = factor(KPT_m@meta.data$new_clusters, levels = my_levels)

KPT_m$new_clusters[Gob] = 7
KPT_m$new_clusters[EEC] = 8

Idents(KPT_m) = factor(KPT_m@meta.data$new_clusters, levels = my_levels)

DimPlot(KPT_m)

```

#### Plot
```{r}
KPT_m = NormalizeData(KPT_m, assay = "RNA")
KPT_m = ScaleData(KPT_m, assay = "RNA")
DefaultAssay(KPT_m) = "RNA"

pdf("2_Full annotation/plots/20210209_SCT_HuOrgKPT_m_UMAP2.pdf")
DimPlot(KPT_m, reduction = "umap", group.by = "treat")
DimPlot(KPT_m, reduction = "umap", split.by = "treat")
DimPlot(KPT_m, reduction = "umap", group.by = "array")
DimPlot(KPT_m, reduction = "umap", group.by = "donor")
DimPlot(KPT_m, reduction = "umap", label = T) + NoLegend()
FeaturePlot(KPT_m, features = c("percent.mt", "nFeature_RNA", "nCount_RNA"), reduction = "umap")
VlnPlot(KPT_m, features = c("percent.mt", "nFeature_RNA", "nCount_RNA"), pt.size = 0)
VlnPlot(KPT_m, features = c("LYZ", "FABP1", "TFF3", "MKI67", "CHGA", "ASCL2"), pt.size = 0)
# WAE marker?
VlnPlot(KPT_m, features = c("CD55", "CDX2", "DUOX2", "FABP1"), pt.size = 0)
# Stem markers
VlnPlot(KPT_m, features = c("SLC12A2", "OLFM4", "CLU", "LRIG1", "ANXA1"), pt.size = 0)
VlnPlot(KPT_m, features = c("EPCAM"), pt.size = 0)
VlnPlot(KPT_m, features = c("APOA1", "BEST4", "GSTA1", "CLCA1", "LCN2"), pt.size = 0)
dev.off()

```

#### Figure out what the clusters are
```{r}

# Cluster DE
KPT_6.response = FindMarkers(KPT_m, ident.1 = 6, logfc.threshold = 0, test.use = "wilcox", min.pct = 0.2, assay = "RNA")

KPT_6.response.filter = KPT_6.response %>% rownames_to_column(var = "gene") %>%
  dplyr::filter(abs(avg_logFC) > 2*sd(KPT_6.response$avg_logFC)) %>%
  dplyr::filter(p_val_adj <  0.05)

KPT_45.response = FindMarkers(KPT_m, ident.1 = c(4,5), logfc.threshold = 0, test.use = "wilcox", min.pct = 0.2, assay = "RNA")

KPT_45.response.filter = KPT_45.response %>% rownames_to_column(var = "gene") %>%
  dplyr::filter(abs(avg_logFC) > 2*sd(KPT_45.response$avg_logFC)) %>%
  dplyr::filter(p_val_adj <  0.05)

KPT_4v5.response = FindMarkers(KPT_m, ident.1 = 4, ident.2 = 5, logfc.threshold = 0, test.use = "wilcox", min.pct = 0.2, assay = "RNA")

KPT_4v5.response.filter = KPT_4v5.response %>% rownames_to_column(var = "gene") %>%
  dplyr::filter(abs(avg_logFC) > 2*sd(KPT_4v5.response$avg_logFC)) %>%
  dplyr::filter(p_val_adj <  0.05)

# GSEA
myGsc.h = loadGSC(file = "2_Full annotation/marker_genes/mSigDB/h.all.v7.0.symbols.gmt", type = "auto") #h Halmark

fc.GSEA.KPT_6.response = data.frame(KPT_6.response$avg_logFC)
rownames(fc.GSEA.KPT_6.response) = rownames(KPT_6.response)

GSEA.h = runGSA(geneLevelStats = fc.GSEA.KPT_6.response,
                 gsc = myGsc.h, gsSizeLim = c(25,500), geneSetStat = "gsea")
sum.GSEA.h = GSAsummaryTable(GSEA.h, save = T, file = "2_Full annotation/GSEA_KPT_6_msigdb.h.all.v7.xls")

fc.GSEA.KPT_45.response = data.frame(KPT_45.response$avg_logFC)
rownames(fc.GSEA.KPT_45.response) = rownames(KPT_45.response)

GSEA.h = runGSA(geneLevelStats = fc.GSEA.KPT_45.response,
                 gsc = myGsc.h, gsSizeLim = c(25,500), geneSetStat = "gsea")
sum.GSEA.h = GSAsummaryTable(GSEA.h, save = T, file = "2_Full annotation/GSEA_KPT_45_msigdb.h.all.v7.xls")

fc.GSEA.KPT_4v5.response = data.frame(KPT_4v5.response$avg_logFC)
rownames(fc.GSEA.KPT_4v5.response) = rownames(KPT_4v5.response)

GSEA.h = runGSA(geneLevelStats = fc.GSEA.KPT_4v5.response,
                 gsc = myGsc.h, gsSizeLim = c(25,500), geneSetStat = "gsea")
sum.GSEA.h = GSAsummaryTable(GSEA.h, save = T, file = "2_Full annotation/GSEA_KPT_4v5_msigdb.h.all.v7.xls")
```

#### QC plots
```{r}
#find markers
KPT_m.markers = FindAllMarkers(KPT_m, assay = "RNA", only.pos = T)
top10 = KPT_m.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)

pdf("2_Full annotation/plots/20210210_SCT_HuOrgKPT_m_QC.pdf")
VlnPlot(KPT_m, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0)
VlnPlot(KPT_m, features = "nFeature_RNA", ncol = 3, group.by = "array", pt.size = 0) + NoLegend()
VlnPlot(KPT_m, features = "nCount_RNA", ncol = 3, group.by = "array", pt.size = 0) + NoLegend()
VlnPlot(KPT_m, features = "percent.mt", ncol = 3, group.by = "array", pt.size = 0) + NoLegend()
DoHeatmap(KPT_m, top10$gene, assay = "RNA", raster = F)
dev.off()

table(KPT_m$treat)
```

#### Start naming clusters
```{r}

# 0
  "progenitor"
  "#bab2ed"
# 1
  "enterocyte"
  "#2C60AD"
# 2
  "stem G1S"
  "#7CC24F"
# 3
  "stem G2M"
  "#32601F"
# 4
  "WAE-like"
  "#9580ed"
# 5
  "DUOX2+ WAE-like"
  "#ed80d3"
# 6
  "quiescent progenitor"
  '#DCE34E'
# 7
  "goblet"
  "#FF4027"
# 8 
  "enteroendocrine"
  "#F79538"
  

```

#### annotate clusters & find DE genes
```{r}
new.cluster.ids = c("progenitor","enterocyte","stem G1S","stem G2M",
                    "WAE-like","DUOX2+ WAE-like","quiescent progenitor",
                    "goblet","enteroendocrine")

names(new.cluster.ids) = levels(KPT_m)
KPT_m = RenameIdents(KPT_m, new.cluster.ids)

my_levels = c("stem G2M", "stem G1S",
              "progenitor", "enterocyte", "WAE-like","DUOX2+ WAE-like",
              "quiescent progenitor", "goblet", "enteroendocrine")

KPT_m@active.ident = factor(KPT_m@active.ident, levels = my_levels)
KPT_m$annotate = Idents(KPT_m)

#Set colors
KPT_colors = c("#32601F", "#7CC24F","#bab2ed","#2C60AD","#9580ed","#ed80d3",'#DCE34E',"#FF4027","#F79538")

#find markers
KPT_m.markers = FindAllMarkers(KPT_m, assay = "RNA", min.pct = 0.2, logfc.threshold = 0.5, only.pos = T)
top10 = KPT_m.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
top5 = KPT_m.markers %>% group_by(cluster) %>% top_n(5, avg_logFC)
write.csv(KPT_m.markers, "2_Full annotation/HuOrgKPT_m_markers_2102021.csv")
ds_cells = Cells(subset(KPT_m, downsample = 50))

KPT_m$percent.mt = PercentageFeatureSet(KPT_m, pattern = "^MT-")
KPT_m$t_d = paste(KPT_m$treat, KPT_m$donor, sep = '_')

T_array_cols = c('#D1D1CF', '#AAAAA9', '#666666', '#E25454', '#EB2626', '#AF4141')

# Plot
pdf("2_Full annotation/plots/20210211_SCT_HuOrgKPT_m_ANNOTATE.pdf", useDingbats = F)
DimPlot(KPT_m, reduction = "umap", label = T, cols = KPT_colors) + NoLegend()
DimPlot(KPT_m, reduction = "umap", split.by = "donor", cols = KPT_colors)
DimPlot(KPT_m, reduction = "umap", split.by = "treat", cols = KPT_colors)
DoHeatmap(KPT_m, top10$gene, ds_cells, raster = F, label = F, assay = "RNA", group.colors = KPT_colors) +
  scale_fill_viridis(option = "B")
VlnPlot(KPT_m, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0, cols = KPT_colors)
VlnPlot(KPT_m, features = "nFeature_RNA", ncol = 3, group.by = "array", pt.size = 0) + NoLegend()
VlnPlot(KPT_m, features = "nCount_RNA", ncol = 3, group.by = "array", pt.size = 0) + NoLegend()
VlnPlot(KPT_m, features = "percent.mt", ncol = 3, group.by = "array", pt.size = 0) + NoLegend()
dev.off()

pdf("2_Full annotation/plots/20210211_SCT_HuOrgKPT_m_QC2.pdf", useDingbats = F, width = 3, height = 3)

VlnPlot(KPT_m, features = c("nFeature_RNA"), pt.size = 0, cols = KPT_colors) +
  NoLegend() + geom_hline(aes(yintercept = 500), linetype = 2) + ylim(0, 7000)
VlnPlot(KPT_m, features = c("nCount_RNA"), pt.size = 0, cols = KPT_colors) + 
  NoLegend() + geom_hline(aes(yintercept = 30000), linetype = 2) + ylim(0, 31000)
VlnPlot(KPT_m, features = c("percent.mt"), pt.size = 0, cols = KPT_colors, y.max = 40) + 
  NoLegend() + geom_hline(aes(yintercept = 35), linetype = 2)

VlnPlot(KPT_m, features = "nFeature_RNA", group.by = "t_d", pt.size = 0, cols = T_array_cols) +
  NoLegend() + geom_hline(aes(yintercept = 500), linetype = 2) + ylim(0, 7000)
VlnPlot(KPT_m, features = "nCount_RNA", group.by = "t_d", pt.size = 0, cols = T_array_cols) + 
  NoLegend() + geom_hline(aes(yintercept = 30000), linetype = 2) + ylim(0, 31000)
VlnPlot(KPT_m, features = "percent.mt", group.by = "t_d", pt.size = 0, cols = T_array_cols, y.max = 40) + 
  NoLegend() + geom_hline(aes(yintercept = 35), linetype = 2)

dev.off

table(KPT_m@meta.data$t_d)
table(KPT_m@meta.data$annotate)

```

#### Examine dataset for marker sets
```{r}

#Wang Markers
nbin = 25
ctrl = 100
EEC_markers = read.table("2_Full annotation/marker_genes/Wang2020_genes/EEC_S6.txt", header = F)
KPT_m = AddModuleScore(KPT_m, EEC_markers, nbin = nbin, ctrl = ctrl, name = "EEC")
KPT_m$EEC1 = rescale(KPT_m$EEC1)
Ent_markers = read.table("2_Full annotation/marker_genes/Wang2020_genes/Enterocyte_S5.txt", header = F)
KPT_m = AddModuleScore(KPT_m, Ent_markers, nbin = nbin, ctrl = ctrl, name = "Ent")
KPT_m$Ent = rescale(KPT_m$Ent1)
Progen_markers = read.table("2_Full annotation/marker_genes/Wang2020_genes/Progenitor_S4.txt", header = F)
KPT_m = AddModuleScore(KPT_m, Progen_markers, nbin = nbin, ctrl = ctrl, name = "Progen")
KPT_m$Progen = rescale(KPT_m$Progen1)
Gob_markers = read.table("2_Full annotation/marker_genes/Wang2020_genes/Goblet_S8.txt", header = F)
KPT_m = AddModuleScore(KPT_m, Gob_markers, nbin = nbin, ctrl = ctrl, name = "Gob")
KPT_m$Gob1 = rescale(KPT_m$Gob1)
Pan_markers = read.table("2_Full annotation/marker_genes/Wang2020_genes/PanethSI_S7.txt", header = F)
KPT_m = AddModuleScore(KPT_m, Pan_markers, nbin = nbin, ctrl = ctrl, name = "Pan")
KPT_m$Pan1 = rescale(KPT_m$Pan1)
Stem_markers = read.table("2_Full annotation/marker_genes/Wang2020_genes/Stem_S3.txt", header = F)
KPT_m = AddModuleScore(KPT_m, Stem_markers, nbin = nbin, ctrl = ctrl, name = "Stem")
KPT_m$Stem1 = rescale(KPT_m$Stem1)

G1s_markers = as.data.frame(read.table("2_Full annotation/marker_genes/Wang2020_genes/S_pahse_S9.txt", header = F)[,1])
KPT_m = AddModuleScore(KPT_m, G1s_markers, nbin = nbin, ctrl = ctrl, name = "G1S")
KPT_m$G1S1 = rescale(KPT_m$G1S1)
G2m_markers = as.data.frame(read.table("2_Full annotation/marker_genes/Wang2020_genes/G2M_phase_S9.txt", header = F)[,1])
KPT_m = AddModuleScore(KPT_m, G2m_markers, nbin = nbin, ctrl = ctrl, name = "G2M")
KPT_m$G2M1 = rescale(KPT_m$G2M1)

# Han adult duodenum markers
GobC_markers = read.table("2_Full annotation/marker_genes/Han2020_genes/Gob_CLCA1_ADuo_S3.txt", header = F)
KPT_m = AddModuleScore(KPT_m, GobC_markers, nbin = nbin, ctrl = ctrl, name = "GobC")
KPT_m$GobC1 = rescale(KPT_m$GobC1)
GobL_markers = read.table("2_Full annotation/marker_genes/Han2020_genes/Gob_LCN2_ADuo_S3.txt", header = F)
KPT_m = AddModuleScore(KPT_m, GobL_markers, nbin = nbin, ctrl = ctrl, name = "GobL")
KPT_m$GobL1 = rescale(KPT_m$GobL1)
EntProg_markers = read.table("2_Full annotation/marker_genes/Han2020_genes/Ent_Prog_ADuo_S3.txt", header = F)
KPT_m = AddModuleScore(KPT_m, EntProg_markers, nbin = nbin, ctrl = ctrl, name = "EntP")
KPT_m$EntP1 = rescale(KPT_m$EntP1)
EntA_markers = read.table("2_Full annotation/marker_genes/Han2020_genes/Ent_APOA1_ADuo_S3.txt", header = F)
KPT_m = AddModuleScore(KPT_m, EntA_markers, nbin = nbin, ctrl = ctrl, name = "EntA")
KPT_m$EntA1 = rescale(KPT_m$EntA1)
EntB_markers = read.table("2_Full annotation/marker_genes/Han2020_genes/Ent_BEST4_ADuo_S3.txt", header = F)
KPT_m = AddModuleScore(KPT_m, EntB_markers, nbin = nbin, ctrl = ctrl, name = "EntB")
KPT_m$EntB1 = rescale(KPT_m$EntB1)
EntG_markers = read.table("2_Full annotation/marker_genes/Han2020_genes/Ent_GSTA1_ADuo_S3.txt", header = F)
KPT_m = AddModuleScore(KPT_m, EntG_markers, nbin = nbin, ctrl = ctrl, name = "EntG")
KPT_m$EntG1 = rescale(KPT_m$EntG1)

# NES genes
NES_markers = as.data.frame(read.table("2_Full annotation/marker_genes/validNESS/NES_genes.txt", header = F)[,1])
KPT_m = AddModuleScore(KPT_m, NES_markers, nbin = nbin, ctrl = ctrl, name = "NES")
KPT_m$NES1 = rescale(KPT_m$NES1)


pdf('2_Full annotation/plots/20210209_SCT_HuOrgKPT_m_MARKERS.pdf', useDingbats = F, width = 3, height = 3)

FeaturePlot(KPT_m, features = c("Stem1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("Progen1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("Ent1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("Pan1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("Gob1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("EEC1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("G2M1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("G1S1"), cols = c("lightgrey", viridis(1)))

FeaturePlot(KPT_m, features = c("GobL1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("EntP1"), cols = c("lightgrey", viridis(1)))
FeaturePlot(KPT_m, features = c("EntB1"), cols = c("lightgrey", viridis(1)))

VlnPlot(KPT_m, features = c("Stem1"), pt.size = 0, cols = KPT_colors) + NoLegend()
VlnPlot(KPT_m, features = c("Progen1"), pt.size = 0, cols = KPT_colors) + NoLegend()
VlnPlot(KPT_m, features = c("G2M1"), pt.size = 0, cols = KPT_colors) + NoLegend()
VlnPlot(KPT_m, features = c("G1S1"), pt.size = 0, cols = KPT_colors) + NoLegend()

VlnPlot(KPT_m, features = c("Gob1"), pt.size = 0, cols = KPT_colors) + NoLegend()
VlnPlot(KPT_m, features = c("EEC1"), pt.size = 0, cols = KPT_colors) + NoLegend()
VlnPlot(KPT_m, features = c("Ent1"), pt.size = 0, cols = KPT_colors) + NoLegend()

VlnPlot(KPT_m, features = c("GobC1","GobL1","EntP1","EntA1", "EntB1", "EntG1"), pt.size = 0, cols = KPT_colors) + NoLegend()

dev.off()

# Other gene markers
pdf('2_Full annotation/plots/20210225_SCT_HuOrgKPT_m_MARKER_genes.pdf', useDingbats = F, width = 3, height = 3)
#WAE markers
VlnPlot(KPT_m, features = c("CD55"), cols = KPT_colors, pt.size = 0) + NoLegend() # WAE marker
VlnPlot(KPT_m, features = c("DUOX2"), cols = KPT_colors, pt.size = 0) + NoLegend() # stress-response marker
VlnPlot(KPT_m, features = c("CLDN4"), cols = KPT_colors, pt.size = 0) + NoLegend() # WAE marker
VlnPlot(KPT_m, features = c("TFF1"), cols = KPT_colors, pt.size = 0) + NoLegend() # WAE marker
VlnPlot(KPT_m, features = c("PDX1"), cols = KPT_colors, pt.size = 0) + NoLegend() # WAE marker
#Stem Markers
VlnPlot(KPT_m, features = c("SLC12A2"), cols = KPT_colors, pt.size = 0) + NoLegend() # stem marker??
VlnPlot(KPT_m, features = c("OLFM4"), cols = KPT_colors, pt.size = 0) + NoLegend() # stem marker
VlnPlot(KPT_m, features = c("LRIG1"), cols = KPT_colors, pt.size = 0) + NoLegend() # Quiesc stem marker
VlnPlot(KPT_m, features = c("PHB"), cols = KPT_colors, pt.size = 0) + NoLegend() # stem / progenitor marker
VlnPlot(KPT_m, features = c("ASCL2"), cols = KPT_colors, pt.size = 0) + NoLegend() # stem / progenitor marker
VlnPlot(KPT_m, features = c("CDK6"), cols = KPT_colors, pt.size = 0) + NoLegend() # stem / progenitor marker
VlnPlot(KPT_m, features = c("MKI67"), cols = KPT_colors, pt.size = 0) + NoLegend()  # cell cycle
#Progenitor markers
VlnPlot(KPT_m, features = c("HES1"), cols = KPT_colors, pt.size = 0) + NoLegend() # HES1 down PC up / Notch related
VlnPlot(KPT_m, features = c("SOX9"), cols = KPT_colors, pt.size = 0) + NoLegend() # progenitor marker
VlnPlot(KPT_m, features = c("LRP6"), cols = KPT_colors, pt.size = 0) + NoLegend() # wnt co-receptor
VlnPlot(KPT_m, features = c("CDX2"), cols = KPT_colors, pt.size = 0) + NoLegend() # enterocyte-related TF
dev.off()


```

#### Save + Load Object
```{r}
saveRDS(KPT_m, '2_Full annotation/SCT_HuOrgKPT_m_20210211.rds', compress= T)
KPT_m = readRDS('2_Full annotation/SCT_HuOrgKPT_m_20210211.rds')
KPT_colors = c("#32601F","#7CC24F","#bab2ed","#2C60AD","#9580ed","#ed80d3",'#DCE34E',"#FF4027","#F79538")
treat_cols = rev(c("#EB2626","#AAAAA9"))

```

#### Extract out identities for plotting
```{r}
# By donor
d.Number.table = data.frame(rbind(table(factor(KPT_m$annotate)[which(KPT_m$donor == '1')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$donor == '3')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$donor  == '4')])))

rownames(d.Number.table) = c("1","3","4")
colnames(d.Number.table) = c("stem_G1S", "stem_G2M",
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine")

d.Number.table = rownames_to_column(d.Number.table, "donor")

d.Plot.table = gather(d.Number.table, "identity", "cell_number", 2:10)
d.Plot.table = d.Plot.table %>% group_by(donor) %>% mutate(cell_frac = cell_number / sum(cell_number))

d.Plot.table$identity = factor(d.Plot.table$identity, levels = rev(c("stem_G2M","stem_G1S", 
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine")))

pdf('2_Full annotation/plots/20210216_HuOrgKPT_m_donor_comp.pdf', useDingbats = F, width = 3, height = 3)
ggplot(d.Plot.table,
       aes(fill=identity, y=cell_number, x=donor, order = identity)) + 
    geom_bar(position="fill", stat = "identity") + 
    scale_fill_manual(values=rev(KPT_colors)) +
    labs(title = "Composition") + theme_classic() + theme(legend.position = "none")
dev.off()

# By donor + treat
Number.table = data.frame(rbind(table(factor(KPT_m$annotate)[which(KPT_m$t_d == 'Ctrl_1')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$t_d == 'Ctrl_3')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$t_d == 'Ctrl_4')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$t_d  == 'KPT_1')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$t_d  == 'KPT_3')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$t_d  == 'KPT_4')])))

rownames(Number.table) = c("C_1","C_3","C_4","K_1","K_3","K_4")
colnames(Number.table) = c("stem_G1S", "stem_G2M",
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine")

Number.table = rownames_to_column(Number.table, "sample")

Plot.table = gather(Number.table, "identity", "cell_number", 2:10)
Plot.table = Plot.table %>% group_by(sample) %>% mutate(cell_frac = cell_number / sum(cell_number))

Plot.table$identity = factor(Plot.table$identity, levels = rev(c("stem_G2M","stem_G1S",
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine")))

Plot.table$sample = factor(Plot.table$sample, levels = c("C_1","K_1","C_3","K_3","C_4","K_4"))

Plot.table = separate(Plot.table, sample, c("treat", "donor"), sep = "_", remove = F)

Plot.table.C = Plot.table %>% dplyr::filter(treat != "K")
Plot.table.K = Plot.table %>% dplyr::filter(treat != "C")

# For fisher's exact test
fisher.table = c()

for(d in unique(pull(Plot.table, donor))) {
  Plot.table.C.d = Plot.table.C %>% dplyr::filter(donor == d)
  Plot.table.K.d = Plot.table.K %>% dplyr::filter(donor == d)
  
  clust.C = Plot.table.C.d %>% dplyr::filter(cell_number > 0)
  clust.K = Plot.table.K.d %>% dplyr::filter(cell_number > 0)
  
  idents = as.character(intersect(pull(clust.C, identity),pull(clust.K, identity)))
  
  for(i in idents) {
  
    IC = sum(as.numeric(dplyr::filter(Plot.table.C.d, identity == i)$cell_number))
    AC = sum(as.numeric(dplyr::filter(Plot.table.C.d, identity != i)$cell_number))
    
    IK = sum(as.numeric(dplyr::filter(Plot.table.K.d, identity == i)$cell_number))
    AK = sum(as.numeric(dplyr::filter(Plot.table.K.d, identity != i)$cell_number))
    
    test_mat = matrix(c(IK, IC, AK, AC), nrow = 2,
       dimnames = list(Treat = c("KPT", "CTRL"),
                       Ident = c(i, "all others")))
    
    fish = fisher.test(test_mat, alternative = "two.sided")
    
    fisher.table = rbind(fisher.table, c(d,i,as.numeric(fish$estimate), fish$conf.int, fish$p.value))
  }
}

colnames(fisher.table) = c("donor", "identity", "odds_ratio", "95_lor", "95_uor", "p_value")
fisher.table = as.data.frame(fisher.table, stringsAsFactors =F)
fisher.table$odds_ratio = as.numeric(fisher.table$odds_ratio)
fisher.table$`95_lor` = as.numeric(fisher.table$`95_lor`)
fisher.table$`95_uor` = as.numeric(fisher.table$`95_uor`)
fisher.table$p_value = as.numeric(fisher.table$p_value)
fisher.table$identity = factor(fisher.table$identity, levels = c("stem_G2M","stem_G1S",
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine"))

fisher.table$adj_p_value = p.adjust(fisher.table$p_value, method = "fdr")

write.csv(fisher.table, '2_Full annotation/huOrg_KPT_m_fisher_test_composition_09102021.csv')

signif1.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.05) %>% dplyr::filter(adj_p_value > 0.01)
signif2.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.01) %>% dplyr::filter(adj_p_value > 0.001)
signif3.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.001) %>% dplyr::filter(adj_p_value > 0.0001)
signif4.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.0001)

pdf('2_Full annotation/plots/20210216_HuOrgKPT_m_donor_treat_comp.pdf', useDingbats = F, width = 3, height = 3)
ggplot(Plot.table,
       aes(fill=identity, y=cell_number, x=sample, order = identity)) + 
    geom_bar(position="fill", stat = "identity") + 
    scale_fill_manual(values=rev(KPT_colors)) +
    labs(title = "Composition") + theme_classic() + theme(legend.position = "none")

ggplot(fisher.table, aes(x = identity, y = odds_ratio, ymin = `95_lor`, ymax = `95_uor`, group = identity)) + 
  geom_pointrange(size = 0.25) + theme_classic() + scale_y_log10() + facet_grid(donor~.) + geom_hline(aes(yintercept = 1), linetype = 2)

dev.off()

# By treat
t.Number.table = data.frame(rbind(table(factor(KPT_m$annotate)[which(KPT_m$treat == 'Ctrl')]),
                   table(factor(KPT_m$annotate)[which(KPT_m$treat  == 'KPT')])))

rownames(t.Number.table) = c("C","K")
colnames(t.Number.table) = c("stem_G1S", "stem_G2M",
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine")

t.Number.table = rownames_to_column(t.Number.table, "treat")

t.Plot.table = gather(t.Number.table, "identity", "cell_number", 2:10)
t.Plot.table = t.Plot.table %>% group_by(treat) %>% mutate(cell_frac = cell_number / sum(cell_number))

t.Plot.table$identity = factor(t.Plot.table$identity, levels = rev(c("stem_G2M","stem_G1S",
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine")))

t.Plot.table.C = t.Plot.table %>% dplyr::filter(treat != "K")
t.Plot.table.K = t.Plot.table %>% dplyr::filter(treat != "C")

# For fisher's exact test
fisher.table = c()
  
ident.C = t.Plot.table.C %>% dplyr::filter(cell_frac > 0.005)
ident.K = t.Plot.table.K %>% dplyr::filter(cell_frac > 0.005)

idents = as.character(semi_join(ident.C[,2], ident.K[,2])$identity)

for (i in idents) {
  IC = as.numeric(dplyr::filter(t.Plot.table.C, identity == i)$cell_number)
  AC = sum(as.numeric(dplyr::filter(t.Plot.table.C, identity != i)$cell_number))
  
  AOC = t(as.numeric(dplyr::filter(t.Plot.table.C, identity != i)$cell_number))
  
  IK = as.numeric(dplyr::filter(t.Plot.table.K, identity == i)$cell_number)
  AK = sum(as.numeric(dplyr::filter(t.Plot.table.K, identity != i)$cell_number))
  
  AOK = t(as.numeric(dplyr::filter(t.Plot.table.K, identity != i)$cell_number))
  
  test_mat = matrix(c(IK, IC, AK, AC), nrow = 2,
     dimnames = list(Treat = c("KPT", "CTRL"),
                     Ident = c(i, "all others")))
  
  test_mat2 = matrix(c(IK, IC, AOK, AOC), nrow = 2,
     dimnames = list(Treat = c("KPT", "CTRL"),
                     Ident = c(i, t(as.character(dplyr::filter(t.Plot.table.C, identity != i)$identity)))))
  
  fish = fisher.test(test_mat, alternative = "two.sided")
  
  fisher.table = rbind(fisher.table, c(i,as.numeric(fish$estimate), fish$conf.int, fish$p.value))
}


colnames(fisher.table) = c("identity", "odds_ratio", "95_lor", "95_uor", "p_value")
fisher.table = as.data.frame(fisher.table, stringsAsFactors =F)
fisher.table$odds_ratio = as.numeric(fisher.table$odds_ratio)
fisher.table$`95_lor` = as.numeric(fisher.table$`95_lor`)
fisher.table$`95_uor` = as.numeric(fisher.table$`95_uor`)
fisher.table$p_value = as.numeric(fisher.table$p_value)
fisher.table$identity = factor(fisher.table$identity, levels = c("stem_G2M","stem_G1S",
              "progenitor", "enterocyte", "WAE_like","DUOX2+_WAE_like",
              "quiescent_progenitor", "goblet", "enteroendocrine"))

fisher.table$adj_p_value = p.adjust(fisher.table$p_value, method = "fdr")

signif1.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.05) %>% dplyr::filter(adj_p_value > 0.01)
signif2.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.01) %>% dplyr::filter(adj_p_value > 0.001)
signif3.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.001) %>% dplyr::filter(adj_p_value > 0.0001)
signif4.fisher.table = fisher.table %>% dplyr::filter(adj_p_value < 0.0001)

pdf('2_Full annotation/plots/20210216_HuOrg_KPT_m_treat_OR.pdf', useDingbats = F, width = 6, height = 2)

ggplot(fisher.table, aes(x = identity, y = odds_ratio, ymin = `95_lor`, ymax = `95_uor`, group = identity)) + 
  geom_pointrange(size = 0.25) + theme_classic() + scale_y_log10() + geom_hline(aes(yintercept = 1), linetype = 2)

dev.off()

```

#### Plots for stem-cell modulation
```{r}
treat_cols = rev(c("#EB2626","#AAAAA9"))
treat_cols2 = c("#EB2626","#AAAAA9", "#AAAAA9")

# stem vs non
KPT_m$stem_v_all = "stem"
KPT_m$stem_v_all[which(KPT_m$annotate == c("stem G2M"))] = "stem G2M"
KPT_m$stem_v_all[which(KPT_m$annotate == c("stem G1S"))] = "stem G1S"
KPT_m$stem_v_all[which(KPT_m$annotate != c("stem G2M", "stem G1S"))] = "non-stem"
stem_v_all.col = c("#AAAAA9", "#7CC24F", "#32601F")

# Look @ NES / Xpo1 stuff
pdf('2_Full annotation/plots/20210217_SCT_HuOrgKPT_m_Xpo1.pdf', useDingbats = F, width = 3, height = 3)

VlnPlot(subset(KPT_m, subset = treat != "KPT"), "XPO1", assay = "RNA", pt.size = 0, cols = KPT_colors) + NoLegend()
VlnPlot(subset(KPT_m, subset = treat != "KPT"), "NES1", pt.size = 0, cols = KPT_colors)+ NoLegend() +
  geom_hline(aes(yintercept = median(subset(KPT_m, subset = treat != "KPT")@meta.data$NES1)), linetype = 2)
VlnPlot(subset(KPT_m, subset = treat != "KPT"), "XPO1", group.by = "stem_v_all", pt.size = 0, assay = "RNA", cols = stem_v_all.col) + NoLegend()
VlnPlot(subset(KPT_m, subset = treat != "KPT"), "NES1", group.by = "stem_v_all", pt.size = 0, cols = stem_v_all.col)+ NoLegend() + 
  geom_hline(aes(yintercept = median(subset(KPT_m, subset = treat != "KPT")@meta.data$NES1)), linetype = 2)
VlnPlot(KPT_m, "XPO1", assay = "RNA", pt.size = 0, split.by = "treat", cols = treat_cols) + NoLegend()
VlnPlot(KPT_m, "XPO1", assay = "RNA", pt.size = 0, group.by = "stem_v_all", split.by = "treat", cols = treat_cols) + NoLegend()
dev.off()

NES_table = FetchData(subset(KPT_m, subset = treat != "KPT"), vars = c("rna_XPO1", "stem_v_all", "NES1"))
NES_table$stem_v_all = as.factor(NES_table$stem_v_all)
DunnettTest(NES1 ~ stem_v_all, data = NES_table, control = "non-stem")

xpo_stemG2M_out = FindMarkers(subset(KPT_m, subset = treat != "KPT"), feature = "XPO1", ident.1 = "stem G2M", ident.2 = "non-stem", group.by = "stem_v_all", test.use = "wilcox", assay = "RNA", verbose = F, logfc.threshold = 0)
xpo_stemG1S_out = FindMarkers(subset(KPT_m, subset = treat != "KPT"), feature = "XPO1", ident.1 = "stem G1S", ident.2 = "non-stem", group.by = "stem_v_all", test.use = "wilcox", assay = "RNA", verbose = F, logfc.threshold = 0)

# sec prog v non
KPT_m$sp_v_all = "all others"
KPT_m$sp_v_all[which(KPT_m$annotate == c("WAE-like"))] = "WAE-like"
KPT_m$sp_v_all[which(KPT_m$annotate == c("DUOX2+ WAE-like"))] = "DUOX2+ WAE-like"
KPT_m$sp_v_all[which(KPT_m$annotate == c("quiescent progenitor"))] = "quiescent progenitor"

sp_v_all.col = c("#AAAAA9","#9580ed", "#ed80d3", '#DCE34E')
KPT_m@meta.data$sp_v_all = factor(x = KPT_m@meta.data$sp_v_all, levels = c("all others", "WAE-like", "DUOX2+ WAE-like", "quiescent progenitor"))

# Look @ LYZ stuff
pdf('2_Full annotation/plots/20210217_SCT_HuOrgKPT_m_LYZ.pdf', useDingbats = F, width = 3, height = 3)

VlnPlot(KPT_m, "LYZ", assay = "RNA", pt.size = 0, group.by = 'donor', split.by = 'treat', cols = treat_cols) + NoLegend()
VlnPlot(KPT_m, "MKI67", assay = "RNA", pt.size = 0, group.by = 'donor', split.by = 'treat', cols = treat_cols) + NoLegend()
VlnPlot(KPT_m, "LYZ", assay = "RNA", pt.size = 0, cols = KPT_colors) + NoLegend()
VlnPlot(KPT_m, "Pan1", pt.size = 0, cols = KPT_colors)+ NoLegend() +
  geom_hline(aes(yintercept = median(KPT_m@meta.data$Pan1)), linetype = 2)

VlnPlot(KPT_m, "LYZ", group.by = "sp_v_all", pt.size = 0, assay = "RNA", cols = sp_v_all.col) + NoLegend()
VlnPlot(KPT_m, "Pan1", group.by = "sp_v_all", pt.size = 0, cols = sp_v_all.col)+ NoLegend() + 
  geom_hline(aes(yintercept = median(KPT_m@meta.data$Pan1)), linetype = 2)
dev.off()

LYZ_td1_out = FindMarkers(KPT_m, feature = "LYZ", ident.1 = "Ctrl_1", ident.2 = "KPT_1", group.by = "t_d", test.use = "wilcox", assay = "RNA", verbose = F, logfc.threshold = 0)
LYZ_td3_out = FindMarkers(KPT_m, feature = "LYZ", ident.1 = "Ctrl_3", ident.2 = "KPT_3", group.by = "t_d", test.use = "wilcox", assay = "RNA", verbose = F, logfc.threshold = 0)
LYZ_td4_out = FindMarkers(KPT_m, feature = "LYZ", ident.1 = "Ctrl_4", ident.2 = "KPT_4", group.by = "t_d", test.use = "wilcox", assay = "RNA", verbose = F, logfc.threshold = 0)

LYZ_sp_out = FindMarkers(KPT_m, feature = "LYZ", ident.1 = "quiescent progenitor", ident.2 = "non-quiescent progenitor", group.by = "sp_v_all", test.use = "wilcox", assay = "RNA", verbose = F, logfc.threshold = 0)

LYZ_DUOX2_out = FindMarkers(KPT_m, feature = "LYZ", ident.1 = "DUOX2+ WAE-like", ident.2 = "WAE-like", group.by = "sp_v_all", test.use = "wilcox", assay = "RNA", verbose = F, logfc.threshold = 0)

```

#### Run Progeny
```{r}
KPT_m = progeny(KPT_m, scale=F, organism="Human", top=300, perm=1, assy_name = "RNA", return_assay = T)
KPT_m = ScaleData(KPT_m, assay = "progeny")

FeaturePlot(KPT_m, features = c("progeny_p53"))

VlnPlot(KPT_m, features = c("progeny_Hypoxia", "progeny_TNFa", "progeny_TGFb"), split.by = "treat", pt.size = 0)

# build out datasets
CellsClusters = data.frame(Cell = names(Idents(KPT_m)), CellType = as.character(Idents(KPT_m)), stringsAsFactors = F)
Treat = data.frame(Cell = rownames(KPT_m@meta.data), Treat = as.character(KPT_m@meta.data$treat), stringsAsFactors = F)

progeny_scores_df = as.data.frame(t(GetAssayData(KPT_m, slot = "scale.data", assay = "progeny"))) %>%
    rownames_to_column("Cell") %>% gather(Pathway, Activity, -Cell)
progeny_scores_df = inner_join(progeny_scores_df, CellsClusters) %>% inner_join(Treat)

#heatmap of all cells
summarized_progeny_scores = progeny_scores_df %>%
    group_by(Pathway, CellType) %>%
    summarise(avg = mean(Activity), std = sd(Activity))

summarized_progeny_scores_df = summarized_progeny_scores %>%
    dplyr::select(-std) %>%
    spread(Pathway, avg) %>%
    data.frame(row.names = 1, check.names = F, stringsAsFactors = F)

summarized_progeny_scores_df = summarized_progeny_scores_df[rev(c("stem G2M","stem G1S",
              "progenitor", "enterocyte", "WAE-like","DUOX2+ WAE-like",
              "quiescent progenitor", "goblet", "enteroendocrine")),]

pdf('2_Full annotation/plots/20210217_HuOrgKPT_m_Progeny_heat.pdf', useDingbats = F, width = 8, height = 4)
superheat(summarized_progeny_scores_df,
          scale = T,
          col.dendrogram = T,
          left.label.col = rev(KPT_colors),
          left.label.text.size = 4,
          left.label.size = 0.3,
          bottom.label.col = "white",
          bottom.label.text.size = 3,
          bottom.label.size = 0.6,
          pretty.order.cols = T,
          bottom.label.text.angle = 90,
          grid.hline.col = "white",
          grid.vline.col = "white",
          heat.pal = viridis(3, option = "B"),
          legend.text.size = 10)
dev.off()

```
